r5r: rapid realistic routing on multimodal transport networks with R5 in R

### 2020-10-26 r-package/paper2020/paper2020.Rmd
back at using poa data in paper

To illustrate functionality, the package includes a small sample data set for 
the city of São Paulo (Brazil). It includes three files:

- An OSM network in `.pbf` format.
- A public transport network in `GTFS.zip` format.
- The spatial coordinates of points covering the area in `.csv` format.

```{r}
# points to directory with data
data_path <- system.file("extdata/spo", package = "r5r")

@@

# read points of origin and destination
points <- fread(file.path(data_path, "spo_hexgrid.csv"))
points <- points[c(sample(1:nrow(points), 100))]
head(points)
```

@@

Often enough one wants more information on the itineraries between 
origin/destination pairs than simply the travel time. For such cases, the 
package includes the `detailed_itineraries()` function, which also takes travel 
restrictions as inputs, but outputs a much more detailed data table at the trip 
segment level. Another key feature of this function is that it (optionally) 
provides multiple alternative routes between origin/destination pairs. The 
algorithm doesn't yet support frequency-based trips (such as São Paulo's), 
however, so we use another data sample included in the package that covers the 
city of Porto Alegre (Brazil):

```{r, message = FALSE}
data_path <- system.file("extdata/poa", package = "r5r")

r5r_core <- setup_r5(data_path)

# load points of interests and set origin and destination
points <- fread(file.path(data_path, "poa_points_of_interest.csv"))
origins <- points[c(10, 14),]
destinations <- points[c(12, 15),]

>>>>

To illustrate functionality, the package includes a small sample data set for 
the city of Porto Alegre (Brazil). It includes three files:

- An OSM network in `.pbf` format.
- A public transport network in `GTFS.zip` format.
- The spatial coordinates of points covering the area in `.csv` format.
- The spatial coordinates of some of the city's points of interest.

```{r}
# points to directory with data
data_path <- system.file("extdata/poa", package = "r5r")

@@

# read points of origin and destination
points <- fread(file.path(data_path, "poa_hexgrid.csv"))
points <- points[c(sample(1:nrow(points), 100))]
head(points)
```

@@

Often enough one wants more information on the itineraries between 
origin/destination pairs than simply the travel time. For such cases, the 
package includes the `detailed_itineraries()` function, which also takes travel 
restrictions as inputs, but outputs a much more detailed data table at the trip 
segment level. Another key feature of this function is that it (optionally) 
provides multiple alternative routes between origin/destination pairs:

```{r, message = FALSE}
# load points of interests and set origin and destination
points <- fread(file.path(data_path, "poa_points_of_interest.csv"))
origins <- points[c(10, 14),]
destinations <- points[c(12, 15),]
